%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Chris}{Ridgers}{Systems \& Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Flay 7, 27-29 Stanley Street
Liverpool, Merseyside L1 6AA
United Kingdom
~
07921573590
~
\href{mailto:chris@digiridge.com}{chris@digiridge.com}
\href{https://chrisridgers.github.io}{https://chrisridgers.github.io}
\href{https://www.facebook.com/chrisridgers}{fb://cridgers}
\href{http://twitter.com/oblivaddict}{tw://oblivaddict}
\section{programming}
{\color{red} $\varheartsuit$} Git, PHP
{\color{red} $\varheartsuit$} PHP, Bash, Ansible
C++, Docker 
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--Now}
{Mashbo}
{Liverpool, UK}
{\emph{Software Engineer} \\
Developed bespoke applications across multiple platforms/ software stacks.  
Maintained and secured production environments on physical and cloud based infrastructure.
Helped develop and iterate internal work processes as part of an ongoing improvement procees.\\
Work duties:
\begin{itemize}
\item Feature development in Symfony Web applications
\begin{itemize}
\item Traditional server applications
\item API development
\item Event driven architecture
\item CLI tools
\end{itemize}
\item Wordpress builds across a multitude of stacks -- currently using Sage 9/ Bedrock
\begin{itemize}
\item Project inheritance / rescue work
\item Public / Private portal applications
\item Woocommerce store sites
\item Systems maintenance:
\begin{itemize}
\item Security patching
\item Automated provisioning of development and production environments
\item Repeatable infrastructure as code: Ansible
\end{itemize}
\end{itemize}
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Part Time}

\begin{entrylist}

\entry
{2013--2014}
{Student Support and Development Services}
{Keele University, Keele UK}
{\emph{Resident Support Assistant} \\
Year long position working within student accommodation as a Resident
Support Assistant (RSA). Roles included: out of hours contact regarding
welfare issues and noise complaints, follow up welfare contact, promoting
friendly living environments among students, arranging regular social activities
and representing the support team at events. Specialist training included:
suicide and self harm awareness, first aid and sexual health awareness.}

%------------------------------------------------

\entry
{2013}
{Keele University w/ JANET}
{Keele University, Keele UK}
{\emph{On-site Conference Assistant} \\
Aided JANET in hosting Networkshop41 at Keele University. Roles included:
directing and assisting visiting conference delegates around the conference
area, promoting the event through social media, assisting with technical
equipment and ensuring arrivals and departures occurred smoothly for delegates
and vendors.}
{\emph{Personal highlights included witnessing a live joint performance by musicians
in both Keele (local) and Scotland (remote) via the JANET network and Low
Latency Audio Visual (LOLA).}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2011--2014} 
{Bachelor of Science {\normalfont Creative Computing \& Music Technology}} 
{Keele University, Keele, UK} 
{\emph{SILO - Sound in Landscape Out} \\ Final year project was an implementation of the Fourier transform to produce 3D terrain objects from music input.} \\
{\emph{Course content:} \\ Computer animation, web design, 3D modelling and animation in Blender, games programming with ODE and OGRE, software requirements engineering, design and evaluation, history of sonic arts, sound recording and mixing with Logic Pro, film soundtrack evolution, visual-audio editing, time/ frequency domain digital signal processing, MAX/MSP application creation /sound synthesis, and music programming using C. Semester abroad studying in Concordia University, Montreal Canada. Awarded 2.1.}

%------------------------------------------------

\entry
{2008--2010}
{BTECH National Diploma {\normalfont Media Production (Games Development)}}
{West Cheshire College, Ellesmere Port, UK}
{Study of the computer games industry, 3D Modelling and Animation (3DS
Max), 2D image and texture creation and game design} \\
{\emph{Course content:} \\
History and overview of the computer games industry, 3D modelling and animation
in 3DSMax, image creation/ manipulation in Adobe Photoshop and
games design and production. Awarded D,D,D.}

%------------------------------------------------

\end{entrylist}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2014}
{Fan Dance 2014, Marshall Force10 and Point-to-Point}
{The S.F Experience, UK}
{In addition to completing the Fan Dance event a second time similarly to the
previous year, I acted as a marshal for two additional events requiring professionalism,
commitment and fitness. These flagship events were the first
from a brand new organisation looking to raise money for soldiers suffering
from combat stress disorders (among other ailments) and provide the public
with an insight in to the gruelling UK special forces selection process.}

%------------------------------------------------

\entry
{2014}
{Fan Dance 2013}
{Talking2Minds, UK}
{Completion of a 24km hiking route typically associated with HRM Special
Forces. Completed on behalf of Talking2Minds and out of respect for the 3
soldiers who died attempting special forces selection during the summer of
2012.}

%------------------------------------------------

\entry
{2011}
{3rd Place Keele 2011 Business Ideas Competition}
{Keele University, UK}
{Won third place for submitting an idea involving students, video games and
the high speed infrastructure of the JANET network.}

%------------------------------------------------

\entry
{2011}
{Silve Duke of Edinburgh Award}
{Air Cadet Force (2247 Hawarden Sqdn.), Hawarden UK}
{Completed (following bronze) with members of the Air Cadet Force. Charity
fund raising work included raising money for the squadron through local
drives, sport activity was shooting (.22 rifles)}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{communication skills}
%
%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{2011}
%{Oral Presentation}
%{California Business Conference}
%{Presented the research I conducted for my Masters of Commerce degree.}
%
%%------------------------------------------------
%
%\entry
%{2010}
%{Poster}
%{Annual Business Conference, Oregon}
%{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%
%%------------------------------------------------
%
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR SECTION
%----------------------------------------------------------------------------------------

\section{Extra Curricular}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--2014}
{Keele University Computing and Innovation, KUCI}
{Keele University, Keele UK}
{Held a range of roles including: Public Relations Officer, Events Manager,
Vice-President and President. Achievements include hosting the end of year
ball at the local Keele hall within the first year of gaining society status, organising
an educational/ professional visit to a third party company event
held in London, increasing member exposure to a professional industry, and
working with the school to improve the classroom computer facilities.}

%------------------------------------------------

\entry
{2011--2014}
{Student Academic Representative, STAR}
{Keele University, Keele UK}
{Filled the voluntary role on and off for a period of 3 years to represent the
students and aid the computing school with collecting feedback in order
to further develop the course to achieve better quality of learning and student
satisfaction. Took a break from the role during a second year semester
studying abroad before returning later that year, before continuing in third
year working with other STAR’s to fill the role.}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} games design and development, operating systems, graphics, 
, system architecture, sound design, recording and synthesis, 
\textbf{personal:} guitar, hiking, video games, film and quality television, 
history, sociology and languages, reading academic texts and sci-fi/ fantasy literature

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}
%
%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography
%
%\printbibsection{book}{books} % Print all books from the bibliography
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
%\end{refsection}
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
%\end{refsection}
%
%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography
%
%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
