%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Chris}{Ridgers}{Systems \& Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
23 Harefields Way
The Wirral
CH49 4SB
United Kingdom
~
07921573590
~
\href{mailto:chris@digiridge.co.uk}{chris@digiridge.co.uk}
\href{https://github.com/chrisRidgers}{gh://chrisRidgers}
\href{https://chrisridgers.github.io}{https://chrisridgers.github.io}
%\href{https://www.facebook.com/chrisridgers}{fb://cridgers}
\href{http://twitter.com/ffsmonty}{tw://ffsmonty}
\section{programming}
{\large \color{red} $\varheartsuit$} Git, PHP
{\color{red} $\varheartsuit$} Bash, Ansible, Docker
C++
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--2020}
{Mashbo}
{Liverpool, UK}
{\emph{Software Engineer} \\
Developed bespoke applications across multiple platforms/ software stacks.  
Maintained and secured production environments on physical and cloud based infrastructure.
Developed and iterated internal work processes as part of an ongoing improvement process.\\
Work duties:
\begin{itemize}
\item Feature development in Symfony Web applications
\begin{itemize}
\item Traditional server applications
\item API development
\item Event driven architecture
\item CLI tools
\end{itemize}
\item WordPress builds across a multitude of stacks -- currently using Sage 9/ Bedrock within a Dockerized build/ deployment system
\item Worked closely with front end developers to facilitate project work and wider platform capabilities.  Particularly with newer WordPress functionality in the post Gutenberg era
\begin{itemize}
\item Project inheritance / rescue work
\item Private portal applications
\item WooCommerce stores
\item Systems maintenance:
\begin{itemize}
\item Security patching
\item Automated provisioning of development and production environments
\item Repeatable infrastructure as code: Ansible
\end{itemize}
\end{itemize}
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\subsection{Part Time}

\begin{entrylist}

\entry
{2013--2014}
{Student Support and Development Services}
{Keele University, Keele UK}
{\emph{Resident Support Assistant} \\
Year long position working within student accommodation as a Resident
Support Assistant (RSA). Roles included: out of hours contact regarding
welfare issues and noise complaints, follow up welfare contact, promoting
friendly living environments among students, arranging regular social activities
and representing the support team at events. Specialist training included:
suicide and self harm awareness, first aid and sexual health awareness.}

%------------------------------------------------

\entry
{2013}
{Keele University w/ JANET}
{Keele University, Keele UK}
{\emph{On-site Conference Assistant} \\
Aided JANET in hosting Networkshop41 at Keele University. Roles included:
directing and assisting visiting conference delegates around the conference
area, promoting the event through social media, assisting with technical
equipment and ensuring arrivals and departures occurred smoothly for delegates
and vendors.}
{\emph{Personal highlights included witnessing a live joint performance by musicians
in both Keele (local) and Scotland (remote) via the JANET network and Low
Latency Audio Visual (LOLA).}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2011--2014} 
{Bachelor of Science {\normalfont Creative Computing \& Music Technology - 2.1}} 
{Keele University, Keele, UK} 
{\emph{SILO - Sound in Landscape Out} \\ Final year project was an implementation of the Fourier transform to produce 3D terrain objects from music input.} \\
{\emph{Course content:} \\ Computer animation, web design, 3D modelling and animation in Blender, games programming with ODE and OGRE, software requirements engineering, design and evaluation, history of sonic arts, sound recording and mixing with Logic Pro, film soundtrack evolution, visual-audio editing, time/ frequency domain digital signal processing, MAX/MSP application creation /sound synthesis, and music programming using C. Semester abroad studying in Concordia University, Montreal Canada.}

%------------------------------------------------

\entry
{2008--2010}
{BTECH National Diploma {\normalfont Media Production (Games Development)}}
{West Cheshire College, Ellesmere Port, UK}
{Study of the computer games industry, 3D Modelling and Animation (3DS
Max), 2D image and texture creation and game design} \\
{\emph{Course content:} \\
History and overview of the computer games industry, 3D modelling and animation
in 3DSMax, image creation/ manipulation in Adobe Photoshop and
games design and production. Awarded D,D,D.}

%------------------------------------------------

\end{entrylist}



%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2019}
{Hub of Hope Ambassador}
{Mashbo, w/ Hub of Hope}
{As part of an ongoing effort to improve ourselves and the industry, Mashbo 
partnered with Hub of Hope to deliver training aimed at de-stigmatising talking
about mental health issues and improve our personal abilities to recognise and 
respond to such issues in our coworkers.}

%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{communication skills}
%
%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{2011}
%{Oral Presentation}
%{California Business Conference}
%{Presented the research I conducted for my Masters of Commerce degree.}
%
%%------------------------------------------------
%
%\entry
%{2010}
%{Poster}
%{Annual Business Conference, Oregon}
%{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%
%%------------------------------------------------
%
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXTRA CURRICULAR SECTION
%----------------------------------------------------------------------------------------

\section{Event Attendance}

\begin{entrylist}

%------------------------------------------------

\entry
{(Covid Permitting) 2021}
{SymfonyCon Disneyland Paris 2021}
{Paris, France}
{Will be attending SymfonyCon to pursue new knowledge relating to the Symfony framework and ecosystem.}


%------------------------------------------------

\entry
{2019}
{SymfonyLive London 2019}
{London, UK}
{Attended SymfonyCon workshops and conference to continue to learn about our favourite framework, and improve my own skills as part of event.}

%------------------------------------------------

\entry
{2019}
{Lead Dev Berlin 2019}
{Berlin, Germany}
{Attended Lead Dev Berlin conference to pursue knowledge relating to development habits and communication skils.  Seeking a broader world view to help recongise exactly where value is delivered to the organisation.}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} games design and development, operating systems, graphics, system architecture, sound design, recording and synthesis. \\
\textbf{personal:} guitar, hiking, video games, film and quality television, World of Warcraft, history, sociology and languages, reading academic texts and sci-fi/ fantasy literature

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}
%
%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography
%
%\printbibsection{book}{books} % Print all books from the bibliography
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
%\end{refsection}
%
%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
%\end{refsection}
%
%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography
%
%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
